paper2_resistance_mechanisms_mixtures

### 2016-06-16 inst/documents/paper2_resistance_mechanisms_mixtures.Rmd
bump version
change to rr_advantage and inputs to 0.2,0.5,0.8

### version 2

@@

For single insecticide use, increasing the values of either effectiveness, exposure, dominance, or selective advantage, all lead to faster resistance (Figs a1-4). (In these four plots the value of the inputs not being varied are set at a constant 0.7 for effectiveness and 0.5 for the other 3).

@@

  i1 <- setInputOneScenario( max_gen = 500,
                      h.RS1_A0 = 0.5, 
                      h.RS2_0B = 0.5,
                      a = a,
                      phi.SS1_A0 = 0.5,
                      phi.SS2_0B = 0.7,
                      s.RR1_A0 = 0.5,
                      s.RR2_0B = 0.5 )

  i2 <- setInputOneScenario( max_gen = 500,
                      h.RS1_A0 = 0.5, 
                      h.RS2_0B = 0.5,
                      a = a,
                      phi.SS1_A0 = 0.7,
                      phi.SS2_0B = 0.7,
                      s.RR1_A0 = 0.5,
                      s.RR2_0B = 0.5 )

  i3 <- setInputOneScenario( max_gen = 500,
                      h.RS1_A0 = 0.5, 
                      h.RS2_0B = 0.5,
                      a = a,
                      phi.SS1_A0 = 0.9,
                      phi.SS2_0B = 0.7,
                      s.RR1_A0 = 0.5,
                      s.RR2_0B = 0.5 )

@@

  exposure <- 0.3
  a <- setExposure(exposure = exposure, insecticideUsed='insecticide1')

  i1 <- setInputOneScenario( max_gen = 500,
                      h.RS1_A0 = 0.5, 
                      h.RS2_0B = 0.5,
                      a = a,
                      exposure = exposure, #used for post-run analysis
                      phi.SS1_A0 = 0.7,
                      phi.SS2_0B = 0.7,
                      s.RR1_A0 = 0.5,
                      s.RR2_0B = 0.5 )

@@

  i2 <- setInputOneScenario( max_gen = 500,
                      h.RS1_A0 = 0.5, 
                      h.RS2_0B = 0.5,
                      a = a,
                      exposure = exposure, #used for post-run analysis
                      phi.SS1_A0 = 0.7,
                      phi.SS2_0B = 0.7,
                      s.RR1_A0 = 0.5,
                      s.RR2_0B = 0.5 )

  exposure <- 0.7
  a <- setExposure(exposure = exposure, insecticideUsed='insecticide1')

  i3 <- setInputOneScenario( max_gen = 500,
                      h.RS1_A0 = 0.5, 
                      h.RS2_0B = 0.5,
                      a = a,
                      exposure = exposure, #used for post-run analysis
                      phi.SS1_A0 = 0.7,
                      phi.SS2_0B = 0.7,
                      s.RR1_A0 = 0.5,
                      s.RR2_0B = 0.5 )

@@

  i1 <- setInputOneScenario( max_gen = 500,
                      h.RS1_A0 = 0.3, 
                      h.RS2_0B = 0.5,
                      a = a,
                      phi.SS1_A0 = 0.7,
                      phi.SS2_0B = 0.7,
                      s.RR1_A0 = 0.5,
                      s.RR2_0B = 0.5 )

  i2 <- setInputOneScenario( max_gen = 500,
                      h.RS1_A0 = 0.5, 
                      h.RS2_0B = 0.5,
                      a = a,
                      phi.SS1_A0 = 0.7,
                      phi.SS2_0B = 0.7,
                      s.RR1_A0 = 0.5,
                      s.RR2_0B = 0.5 )

  i3 <- setInputOneScenario( max_gen = 500,
                      h.RS1_A0 = 0.7, 
                      h.RS2_0B = 0.5,
                      a = a,
                      phi.SS1_A0 = 0.7,
                      phi.SS2_0B = 0.7,
                      s.RR1_A0 = 0.5,
                      s.RR2_0B = 0.5 )

@@

  i1 <- setInputOneScenario( max_gen = 500,
                      h.RS1_A0 = 0.5, 
                      h.RS2_0B = 0.5,
                      a = a,
                      phi.SS1_A0 = 0.7,
                      phi.SS2_0B = 0.7,
                      s.RR1_A0 = 0.3,
                      s.RR2_0B = 0.5 )

  i2 <- setInputOneScenario( max_gen = 500,
                      h.RS1_A0 = 0.5, 
                      h.RS2_0B = 0.5,
                      a = a,
                      phi.SS1_A0 = 0.7,
                      phi.SS2_0B = 0.7,
                      s.RR1_A0 = 0.5,
                      s.RR2_0B = 0.5 )

  i3 <- setInputOneScenario( max_gen = 500,
                      h.RS1_A0 = 0.5, 
                      h.RS2_0B = 0.5,
                      a = a,
                      phi.SS1_A0 = 0.7,
                      phi.SS2_0B = 0.7,
                      s.RR1_A0 = 0.7,
                      s.RR2_0B = 0.5 )

@@

  print( ggplot(df_resist, aes(x=generation, y=resistance, colour=s.RR1_A0)) + 
         labs(colour = "selective advantage") +
         coord_trans(y = "log10") +   
         geom_point() #show.legend=FALSE) +

@@

  cat("Fig. a4. Selective advantage effect on single insecticide.")

@@

```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , s.RR1_A0 = 0.5 , s.RR2_0B = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2') )
cat("Fig. 1. All control inputs equal at 0.5")
```

@@

```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.9 , phi.SS2_0B = 0.5 , s.RR1_A0 = 0.5 , s.RR2_0B = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2') )
cat("Fig. 2. Effectiveness of insecticide1 increased from 0.5 to 0.9")
```

@@

```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.9 , phi.SS2_0B = 0.9 , s.RR1_A0 = 0.5 , s.RR2_0B = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2') )
cat("Fig. 3. Effectiveness of both insecticides 0.9")
```

@@

```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.9 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , s.RR1_A0 = 0.5 , s.RR2_0B = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2') )
cat("Fig. 4. Dominance of insecticide1 0.9")
```

```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.9 , h.RS2_0B = 0.9 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , s.RR1_A0 = 0.5 , s.RR2_0B = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2') )
cat("Fig. 5. Dominance of both insecticides 0.9")
```

**Selective advantage of resistance**
Decreasing the selective advantage of resistance to insecticide1 from 0.5 to 0.1 increases it's time-to-resistance in the mixture from 40 generations to 150, and has a similar effect on it's use in isolation (Fig. 6). However, it has little effect on resistance to insecticide2. Because of this sequential use continues to generate a longer time-to-resistance than the mixture. Decreasing the selective advantage of both alleles to 0.1 results in a longer time-to-resistance of 200 generations for the mixture (Fig. 7), however the relative shape of the resistance curves remains the same as in Fig. 1, with sequential use continuing to generate longer time-to-resistance.

[Increasing the selective advantage of resistance above 0.5 causes an error about fitness values above 1. How to explain this ?]

```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , s.RR1_A0 = 0.1 , s.RR2_0B = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2') )
cat("Fig. 6. Selective advantage of insecticide1 0.1")
```

```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , s.RR1_A0 = 0.1 , s.RR2_0B = 0.1 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2') )
cat("Fig. 7. Selective advantage of both insecticides 0.1")
```

@@

```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , s.RR1_A0 = 0.1 , s.RR2_0B = 0.1 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2') )
cat("Fig. 8. Selective advantage of both insecticides 0.1, effectiveness to 0.7")
```

@@

```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.9 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , s.RR1_A0 = 0.5 , s.RR2_0B = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2') )
cat("Fig. 9. Exposure 0.9")
```

```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.7 , phi.SS2_0B = 0.7 , s.RR1_A0 = 0.5 , s.RR2_0B = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2') )
cat("Fig. 10. Effectiveness 0.7, sequence favoured")
```

```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.9 , phi.SS1_A0 = 0.7 , phi.SS2_0B = 0.7 , s.RR1_A0 = 0.5 , s.RR2_0B = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2') )
cat("Fig. 11. Effectiveness 0.7, Exposure 0.9, mixture favoured")
```

```{r, eval=FALSE, echo=FALSE, fig.height=4}
### 3 examples showing how changing effectiveness can alter the ranking of insecticide strategies
#old modification of curtis values
#### Curtis' Fig 2. inputs : mix2 > adaptive > mix1 > seq
runcurtis_f2( P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.17 , h.RS2_0B = 0.0016 , exposure = 0.9 , phi.SS1_A0 = 0.73 , phi.SS2_0B = 1 , s.RR1_A0 = 0.23 , s.RR2_0B = 0.43 )
```

```{r, eval=FALSE, echo=FALSE, fig.height=4}
#old modification of curtis values
#### decrease effectiveness of I2 from 1 to 0.85 : mix2 > adaptive > seq > mix1
runcurtis_f2( P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.17 , h.RS2_0B = 0.0016 , exposure = 0.9 , phi.SS1_A0 = 0.73 , phi.SS2_0B = 0.85 , s.RR1_A0 = 0.23 , s.RR2_0B = 0.43 )
```

```{r, eval=FALSE, echo=FALSE, fig.height=4}
#old modification of curtis values
#### also decrease effectiveness of I1 from 0.73 to 0.63 : seq > mix2 > adaptive > mix1
runcurtis_f2( P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.17 , h.RS2_0B = 0.0016 , exposure = 0.9 , phi.SS1_A0 = 0.63 , phi.SS2_0B = 0.85 , s.RR1_A0 = 0.23 , s.RR2_0B = 0.43 )
```

>>>>

### version 3

@@

For single insecticide use, increasing the values of either effectiveness, exposure, dominance, or the selective advantage of RR, all lead to faster resistance (Figs a1-4). (In these four plots the value of the inputs not being varied are set at a constant 0.5).

@@

  i1 <- setInputOneScenario( max_gen = 500,
                      h.RS1_A0 = 0.5, 
                      h.RS2_0B = 0.5,
                      a = a,
                      phi.SS1_A0 = 0.2,
                      phi.SS2_0B = 0.5,
                      rr_advantage_I1 = 0.5,
                      rr_advantage_I2 = 0.5 )

  i2 <- setInputOneScenario( max_gen = 500,
                      h.RS1_A0 = 0.5, 
                      h.RS2_0B = 0.5,
                      a = a,
                      phi.SS1_A0 = 0.5,
                      phi.SS2_0B = 0.5,
                      rr_advantage_I1 = 0.5,
                      rr_advantage_I2 = 0.5 )

  i3 <- setInputOneScenario( max_gen = 500,
                      h.RS1_A0 = 0.5, 
                      h.RS2_0B = 0.5,
                      a = a,
                      phi.SS1_A0 = 0.8,
                      phi.SS2_0B = 0.5,
                      rr_advantage_I1 = 0.5,
                      rr_advantage_I2 = 0.5 )

@@

  exposure <- 0.2
  a <- setExposure(exposure = exposure, insecticideUsed='insecticide1')

  i1 <- setInputOneScenario( max_gen = 500,
                      h.RS1_A0 = 0.5, 
                      h.RS2_0B = 0.5,
                      a = a,
                      exposure = exposure, #used for post-run analysis
                      phi.SS1_A0 = 0.5,
                      phi.SS2_0B = 0.5,
                      rr_advantage_I1 = 0.5,
                      rr_advantage_I2 = 0.5 )

@@

  i2 <- setInputOneScenario( max_gen = 500,
                      h.RS1_A0 = 0.5, 
                      h.RS2_0B = 0.5,
                      a = a,
                      exposure = exposure, #used for post-run analysis
                      phi.SS1_A0 = 0.5,
                      phi.SS2_0B = 0.5,
                      rr_advantage_I1 = 0.5,
                      rr_advantage_I2 = 0.5 )

  exposure <- 0.8
  a <- setExposure(exposure = exposure, insecticideUsed='insecticide1')

  i3 <- setInputOneScenario( max_gen = 500,
                      h.RS1_A0 = 0.5, 
                      h.RS2_0B = 0.5,
                      a = a,
                      exposure = exposure, #used for post-run analysis
                      phi.SS1_A0 = 0.5,
                      phi.SS2_0B = 0.5,
                      rr_advantage_I1 = 0.5,
                      rr_advantage_I2 = 0.5 )

@@

  i1 <- setInputOneScenario( max_gen = 500,
                      h.RS1_A0 = 0.2, 
                      h.RS2_0B = 0.5,
                      a = a,
                      phi.SS1_A0 = 0.5,
                      phi.SS2_0B = 0.5,
                      rr_advantage_I1 = 0.5,
                      rr_advantage_I2 = 0.5 )

  i2 <- setInputOneScenario( max_gen = 500,
                      h.RS1_A0 = 0.5, 
                      h.RS2_0B = 0.5,
                      a = a,
                      phi.SS1_A0 = 0.5,
                      phi.SS2_0B = 0.5,
                      rr_advantage_I1 = 0.5,
                      rr_advantage_I2 = 0.5 )

  i3 <- setInputOneScenario( max_gen = 500,
                      h.RS1_A0 = 0.8, 
                      h.RS2_0B = 0.5,
                      a = a,
                      phi.SS1_A0 = 0.5,
                      phi.SS2_0B = 0.5,
                      rr_advantage_I1 = 0.5,
                      rr_advantage_I2 = 0.5 )

@@

  i1 <- setInputOneScenario( max_gen = 500,
                      h.RS1_A0 = 0.5, 
                      h.RS2_0B = 0.5,
                      a = a,
                      phi.SS1_A0 = 0.5,
                      phi.SS2_0B = 0.5,
                      rr_advantage_I1 = 0.2,
                      rr_advantage_I2 = 0.5 )

  i2 <- setInputOneScenario( max_gen = 500,
                      h.RS1_A0 = 0.5, 
                      h.RS2_0B = 0.5,
                      a = a,
                      phi.SS1_A0 = 0.5,
                      phi.SS2_0B = 0.5,
                      rr_advantage_I1 = 0.5,
                      rr_advantage_I2 = 0.5 )

  i3 <- setInputOneScenario( max_gen = 500,
                      h.RS1_A0 = 0.5, 
                      h.RS2_0B = 0.5,
                      a = a,
                      phi.SS1_A0 = 0.5,
                      phi.SS2_0B = 0.5,
                      rr_advantage_I1 = 0.8,
                      rr_advantage_I2 = 0.5 )

@@

  print( ggplot(df_resist, aes(x=generation, y=resistance, colour=rr_advantage_I1)) + 
         labs(colour = "selective advantage") +
         coord_trans(y = "log10") +   
         geom_point() #show.legend=FALSE) +

@@

  cat("Fig. a4. Selective advantage of RR effect on single insecticide.")

@@

```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_advantage_I1 = 0.5 , rr_advantage_I2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2') )
cat("Fig. 1. All control inputs equal at 0.5")
```

@@

```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.9 , phi.SS2_0B = 0.5 , rr_advantage_I1 = 0.5 , rr_advantage_I2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2') )
cat("Fig. 2. Effectiveness of insecticide1 increased from 0.5 to 0.9")
```

@@

```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.9 , phi.SS2_0B = 0.9 , rr_advantage_I1 = 0.5 , rr_advantage_I2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2') )
cat("Fig. 3. Effectiveness of both insecticides 0.9")
```

@@

```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.9 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_advantage_I1 = 0.5 , rr_advantage_I2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2') )
cat("Fig. 4. Dominance of insecticide1 0.9")
```

```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.9 , h.RS2_0B = 0.9 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_advantage_I1 = 0.5 , rr_advantage_I2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2') )
cat("Fig. 5. Dominance of both insecticides 0.9")
```

**Selective advantage of resistance**
#TODO replace Figs 6,7,8 with AA,BB,CC below and modify this text
Decreasing the selective advantage of resistance to insecticide1 from 0.5 to 0.1 increases it's time-to-resistance in the mixture from 40 generations to 150, and has a similar effect on it's use in isolation (Fig. 6). However, it has little effect on resistance to insecticide2. Because of this sequential use continues to generate a longer time-to-resistance than the mixture. Decreasing the selective advantage of both alleles to 0.1 results in a longer time-to-resistance of 200 generations for the mixture (Fig. 7), however the relative shape of the resistance curves remains the same as in Fig. 1, with sequential use continuing to generate longer time-to-resistance.

```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_advantage_I1 = 0.1 , rr_advantage_I2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2') )
cat("Fig. 6. Selective advantage of insecticide1 0.1")
```

```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_advantage_I1 = 0.1 , rr_advantage_I2 = 0.1 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2') )
cat("Fig. 7. Selective advantage of both insecticides 0.1")
```

@@

```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_advantage_I1 = 0.1 , rr_advantage_I2 = 0.1 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2') )
cat("Fig. 8. Selective advantage of both insecticides 0.1, effectiveness to 0.7")
```

#cool contrast between these scenarios modifying effectiveness and rr_advantage in which all defaults set to 0.5 except
TODO incorporate this into text above

#AA effectiveness I1 to 0.8 causes mixture to be slower, although I1 is faster it protects I2 in mixture, making mixture slower
```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.8 , phi.SS2_0B = 0.5 , rr_advantage_I1 = 0.5 , rr_advantage_I2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2') )
cat("Fig. AA. effectiveness to 0.8")
```

#BB rr advantage I1 to 0.8 sequential remains slower, although I1 is faster as in previous it provides less protection to I2 in the mixture
```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_advantage_I1 = 0.8 , rr_advantage_I2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2') )
cat("Fig. BB rr_advantage I1 0.8")
```

#CC rr advantage I2 to 0.2 sequential remains slower (just), I2 slower than I1 in mixture similar to AA but receives less protection in mixture
```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_advantage_I1 = 0.5 , rr_advantage_I2 = 0.2 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2') )
cat("Fig. CC. rr_advantage I2 0.2")
```

@@

```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.9 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_advantage_I1 = 0.5 , rr_advantage_I2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2') )
cat("Fig. 9. Exposure 0.9")
```

```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.7 , phi.SS2_0B = 0.7 , rr_advantage_I1 = 0.5 , rr_advantage_I2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2') )
cat("Fig. 10. Effectiveness 0.7, sequence favoured")
```

```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.9 , phi.SS1_A0 = 0.7 , phi.SS2_0B = 0.7 , rr_advantage_I1 = 0.5 , rr_advantage_I2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2') )
cat("Fig. 11. Effectiveness 0.7, Exposure 0.9, mixture favoured")
```
